<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{1. A data set in rrecsys}
-->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## The Rating Matrix

First thing first, to use a RS you should start from a data set, more specifically a rating matrix. In this case rrecsys is built to start process any available matrix as long as the user has a clear idea of the composition of its rating matrix. In a rating matrix all 0 or NULL values will be considered as missing values. The users will be on rows and the items will be on columns. 
Currently rrecsys is equipped with the [MovieLens Latest](http://grouplens.org/datasets/movielens/latest/) dataset. We will use this dataset for demonstration. To load it:
```{r, message=FALSE}
library(rrecsys)
data("mlLatest100k")
```
To define a Likert scale data set a user would have to specify the domain of the ratings, _minimum_ and _maximum_ of the ratings. The precision of the rating, currently in rrecsys is either half star or full scale (argument _halfStar_). For example:
```{r}
ML <- defineData(mlLatest100k, minimum = .5, maximum = 5, halfStar = TRUE)
ML
```
A dataset can be as well binarized by:
```{r}
binML <- defineData(mlLatest100k, binary = TRUE, goodRating = 3)
binML
```
In this case all the rating in mlLatest100k with a value larger or equal to _goodRating_ are converted to 1 and the resto to 0. This conversion has no scientific relevance, just used for demonstration purposes on OCCF.
The output of _defineData_ is an S4 object (class _dataSet_). This would be the main input to the dispatcher in rrecsys for training a model.
A _dataSet_ object can be explored with the following methods:
```{r, eval=FALSE}
# Number of times an item was rated.
colRatings(ML)
# Number of times a user has rated.
rowRatings(ML)
# Total number of rating in the rating matrix.
numRatings(ML)
# Sparsity.
sparsity(ML)
```
A _dataSet_ object can be cropped to contain a specific number of ratings:
```{r}
# Removing users that rated less than 40 items and items that were rated less than 30 times.
subML <- ML[rowRatings(ML)>=40, colRatings(ML)>=30]
sparsity(ML)
sparsity(subML)
```
