<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{2.2 Item-based k-nearest neighbors}
-->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rrecsys)
data("mlLatest100k")
ML <- defineData(mlLatest100k, minimum = .5, maximum = 5, halfStar = TRUE)
smallML <- ML[rowRatings(ML)>=250, colRatings(ML)>=150]
```

## Item-based k-nearest neighbors in rrecsys

Given a target user and her positively rated items, the algorithm will identify the k-most similar items for each target _a_ and will rank them according to aggregated similarities with the different targets as described by Sarwar et al. The similarity is measured based on three algorithms: cosine(simFunct =1), adjuted cosine(simFunct = 2) and Pearson Correlation(simFunct = 3).

To train a model with this algorithm is required to define an additional argument, _neigh_ the neighborhood size.
```{r}
ibknn <- rrecsys(smallML, "ibknn", simFunct = 1, neigh = 20)
ibknn
```
The _neigh_ default value is 10.

The returned object is of type _IBclass_. 

To get more details about the slots read the reference [manual](https://cran.r-project.org/web/packages/rrecsys/rrecsys.pdf).

