<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{3.1 Predicting & recommending}
-->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rrecsys)
data("mlLatest100k")
ML <- defineData(mlLatest100k, minimum = .5, maximum = 5, halfStar = TRUE)
smallML <- ML[rowRatings(ML)>=200, colRatings(ML)>=100]
svd <- rrecsys(smallML, "FunkSVD", k = 10, gamma = .015, lambda = .001)
ibknn <- rrecsys(smallML, "ibknn", simFunct = 1, neigh = 20)
```

## Predicting & recommending

Once a model has been trained rrecsys may be used to generate either recommendation or predictions. 

The prediction method will generate a new rating matrix with estimations on the missing ratings. Let’s predict using two models trained in the previous vignettes:
```{r}
pSVD <- predict(svd)
pIB <- predict(ibknn)
# Lets compare predicted results for user 1, 4 and 7 on two movies:
pSVD[c(1,4,6), c("Jumanji (1995)", "GoldenEye (1995)")]
pIB[c(1,4,6), c("Jumanji (1995)", "GoldenEye (1995)")]
```
The _predict_ method has a second argument, _Round_ that rounds predicted values to the scale and binds them to the domain of the data set.

The _recommend_ method generates a top-N list for each user:
```{r}
rSVD <- recommend(svd, topN = 3)
rIB <- recommend(ibknn, topN = 3)
# Let’s compare results on user 3:
rSVD[4]
rIB[4]
```
The _topN_ argument specifies the length of the recommended list for each user.
