<!--
%\VignetteEngine{knitr::knitr}
%\VignetteIndexEntry{2. Dispacher and registry}
-->

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Dispatcher

Similar to other packages in R (i.e.: proxy, recommenderlab, etc.), rrecsys uses a formal method in combination to a registry to execute a specific function. The non-primitive function _rrecsys_ will process only S4 object of type _dataSet_ and based on its function definition will determine whatever the required algorithms is available in the registry. Resuming, has two main arguments, the dataset (_data_), and the algorithm name (_alg_, which isn't case sensitive and might be matched even partially) the rest are the ellipses which depend on the required algorithm:
```{r, eval=FALSE}
# Usage
rrecsys(data, alg, ...)
```
The method _rrecsys_ will train model on the given dataset with the required method and its configuration.
In the next vignettes will be given more details about the possible alternative arguments for the dispatcher.


## The registry
The registry is a structure that may be used even autonomously. The main function of registry would be to display available recommender algorithms in rrecsys and theirs default configuration. To call it:
```{r,message=FALSE}
library(rrecsys)
```
```{r}
rrecsysRegistry
```
